---
title: "Final Project"
author: "Anujeeth Veerla"
date: "08/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Installing required libraries
```{r}
library(factoextra)
library(tidyverse)
library(cluster)
```

#Reading data from CSV file
```{r}
Countries<-read.csv("Country-data.csv")
head(Countries)
```

#Removing categorical column and taking only numericals columns
```{r}
Countries_df<-as.data.frame(Countries)
rownames(Countries_df)<-Countries_df[,1]
head(Countries_df)
```

#Removing non-quantitative variable (country column which is the 1st column and taking 2to10 columns) from csv
```{r}

Countries_df<-Countries_df[,2:10]
head(Countries_df)
```

#Now we're scaling the data which is having quantitative variables only
```{r}

Countries_scale<-scale(Countries_df)
#Printing the scaled data
head(Countries_scale)
```

#Calculate K value using Elbow and Silhouette method
```{r}
fviz_nbclust(Countries_scale,kmeans, method = "wss")+labs(subtitle = "Elbow Method")
fviz_nbclust(Countries_scale,kmeans, method = "silhouette")+labs(subtitle = "Silhouette Method")
set.seed(1)
#Taking the K value as 3 and 25 iterations
Kmeans3<-kmeans(Countries_scale, centers = 3, nstart = 25)
Kmeans3$centers
```

#Visualizing the clusters
```{r}
fviz_cluster(Kmeans3, data = Countries_scale, main = "Clustering with K=3")
fit<-kmeans(Countries_scale,3)
```

#Now, calculating the mean value of all quantitative variables to analyze the clusters
```{r}
aggregate(Countries_scale, by=list(fit$cluster), FUN=mean)
FitData<-data.frame(Countries_scale,fit$cluster)
FitData
```


#Filtering the countries which belongs to cluster 1 and displaying the results
```{r}
Group1<-filter(FitData,fit.cluster==1)
#Viewing the list of countries in cluster1 which need immediate HELP
Group1
HelpNeededCountries<-Group1[,0]
HelpNeededCountries
```

#Trying with K=4
```{r}
Kmeans4<-kmeans(Countries_scale, centers = 4, nstart = 25)
Kmeans4$centers
```

#Visualizing the clusters when k=4
```{r}
library(cluster)
fviz_cluster(Kmeans4, data = Countries_scale, main = "Clustering with K=4")
fit4<-kmeans(Countries_scale,4)
```


#Calculating mean value for 4 clusters
```{r}
aggregate(Countries_scale, by=list(fit4$cluster), FUN=mean)
FitData4<-data.frame(Countries_scale,fit4$cluster)
FitData4
```

```{r}
#Filtering the countries which belongs to cluster 3
Group3<-filter(FitData4,fit4.cluster==3)
#Viewing the list of countries in cluster3 which need immediate HELP
Group3
HelpNeededCountriesk3<-Group3[,0]
HelpNeededCountriesk3
```

#Trying with K=5
```{r}
Kmeans5<-kmeans(Countries_scale, centers = 5, nstart = 25)
Kmeans5$centers
```

#Visualizing the clusters when k=5
```{r}
fviz_cluster(Kmeans5, data = Countries_scale, main = "Clustering with K=5")
fit5<-kmeans(Countries_scale,5)
```


#Calculating mean value for 5 clusters
```{r}
aggregate(Countries_scale, by=list(fit5$cluster), FUN=mean)
FitData5<-data.frame(Countries_scale,fit5$cluster)
FitData5
```
#Filtering the countries which belongs to cluster 1
```{r}
Group1<-filter(FitData5,fit5.cluster==1)
#Viewing the list of countries in cluster1 which need immediate HELP
Group1
HelpNeededCountriesk5<-Group1[,0]
HelpNeededCountriesk5
```
#Conclusion: After clustering with K=3,4,5 it seems 3 is the best fit. And in cluster 1, there are 47 countries which need immediate help. 






